Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-11-09 manuscript/text_reuse.tex

In this paper we address these issues and evaluate how much policy overlap can
be detected using text reuse measures. Following Wilkerson et al. (2015) we use
supervised machine learning to separate boiler plate from substantive text. We
further more use an original data set on policy diffusion to evaluate how much
equivalent policy can be detected using measures of text reuse. Using the system
developed by Burges et al. (2015) we calculate text reuse scores for all pairs
of bills in our dataset. We then use these scores in a model that classifies
bills as equivalent and evaluate its performance with the validation data set.

@@

[This might be overlapping a bit with your part]

@@

In order to detect text reuse between bills we follow \citet{wilkerson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.

\subsection{Tasks}
\begin{itemize}
\item Policy diffusion (FL expand paragraph)
\item Text re-use in CBP in bills 
\item Text re-use in general
\begin{itemize}
\item Plaigirism
\item Alignment (FL expand review of Wilkerson et al)

\citet{wilkerson2015tracing} use the

\end{itemize} 
\item Discussion of text-based classification
\end{itemize}

@@

Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 10 words). Alignments between almost all bills are found and most of the alignments are procedural language. This is apparent in Figure \ref{fig:state_to_state} which displays the average alignment score for bills from Illinois (left panel) and Washington (right panel) for all other states in the sampled data set (x-axis). Especially for Illinois there is a much higher alignment score for bills from the same state. This shows that a minimum threshold and a classifier for procedural language are necessary.

@@

In order to make the computation more feasible, we rely on a similar strategy as \citet{wilkerson2015tracing}. Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents. Since the seraching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre selection of similar bills that are then exhaustively checked for text reuse:

@@

\begin{itemize}
    \item Augment the timing dataset with the document similarity scores
    \item

>>>>

In this paper we address these issues and evaluate how much policy overlap can
be detected using text reuse measures. Following Wilkerson et al. (2015) we use
supervised machine learning to separate boiler plate from substantive text. We
further more use an original data set on policy diffusion to evaluate how much
equivalent policy can be detected using measures of text reuse. Using the system
developed by Burges et al. (2015) we calculate text reuse scores for all pairs
of bills in our dataset.

We will then assess the scientific value of the text reuse scores in several different ways. First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text. Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Third, we assess the how well policy diffusion networks that have been established by previous research can be discovered using the amount of text reuse between states. And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.

@@

@@

Previous research on policy diffusion relies almost exclusively on small subsamples of legislation and hand coded data. Little work has been invested in investigating automated ways of detecting equivalent bills in order to measure policy diffusion. 
\citet{wilkerson2015tracing} use the Smith-Waterman local alignment algorithm 
\citep{smith1981identification} to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US congress.

\subsection{Tasks}
\begin{itemize}
\item Discuss and find some literature on copying legislative language: 
    \begin{itemize}
        \item Interest groups and model legislation
        \item Legislator's resources
    \end{itemize}
\item Policy diffusion (FL expand paragraph)
\item Text re-use in CBP in bills 
\item Text re-use in general
\item Alignment (FL expand review of Wilkerson et al)
\item Discussion of text-based classification
\end{itemize}

@@

Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 5 matching 10-grams). Alignments between almost all bills are found and most of the alignments are procedural language. This is apparent in Figure \ref{fig:state_to_state} which displays the average alignment score for bills from Illinois (left panel) and Washington (right panel) for all other states in the sampled data set (x-axis). Especially for Illinois there is a much higher alignment score for bills from the same state. This shows that a minimum threshold and a classifier for procedural language are necessary.

@@

In order to make the computation more feasible, we rely on a similar strategy as \citet{wilkerson2015tracing}. Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents. Since seaching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre-selection of similar bills that are then exhaustively checked for text reuse:

@@

\begin{itemize}
    \item For the 1000 bill sample, retrieve the 100 most similar bills from the database 
    \item Calculate the alignments between the focus bills and the retrieved bills
    \item Assess the relationship of the search score with the alignment scores
\end{itemize}
